---
title: "Columbia Psychology Research Assistant Recruitment"
---

```{r setup, include=FALSE}
library(kableExtra)
options(kableExtra.html.bsTable = TRUE)
library(tidyverse)
```

# Welcome!

***

We believe that the chance to participate in research is one of the best opportunities that our department has to offer.  By joining a lab, you will see how research projects are developed, how data is analyzed, and how presentations are put together for conferences and publication.  If you are involved in a lab for the long term, you may even contribute to a project that enables you to be a published researcher yourself.  

More information about specific labs is available at the links at the bottom of this page These pages have been curated just for *you* to let you know what each lab would expect from you and what you could expect from them. You can find each lab's more general-purpose website [here](https://psychology.columbia.edu/content/lab-websites)

This website is meant to act as an asynchronous extension of our typical Lab Preview Day. The recruitment videos, blurbs, and contact info on this website are meant to let you know who is actively recruiting at the moment and how to reach out to them. The website will be updated throughout the year as the needs of labs change, so even if labs aren't recruiting at the moment they may be in the future.


## Ways to be involved

***
 
There are three ways to get involved in a research lab:
 
### 1) Volunteer
Many students volunteer in research labs.  Some labs require that students volunteer for a period of time before becoming more “official” members of the lab.
 
### 2) Register for Supervised Individual Research (PSYC 3950) 
Many students register for supervised research.  You may register for up to 4 points of supervised research per term.  In general, you should figure that you will be working in a lab for approximately 3 hours per week per credit.  This is not set in stone and must be negotiated with the specific lab that you will be working in.  Different labs have slightly different requirements.  As part of your supervised research, you will be expected to do some independent academic work related to the lab work you are doing.  This may be a paper or an oral presentation, depending on the lab.
 
### 3) Work-study/Paid work 
Sometimes labs will hire undergraduates as work-study students to work in their labs.  Occasionally non-work study positions are available for students with very special skills that are needed (e.g., programming).  This must be arranged with a particular lab on an individual basis.


## Lab Information

***

```{r, echo = F, warning = F}
library(knitr)
labs <- read_delim("../static/lab-info.txt", delim = "\t", show_col_types = FALSE) %>%
  mutate(Lab = paste0("[", Lab_only, "](", urls, ")")) %>%
  mutate("Recruiting Fall 2021" = RAs)


options(kableExtra.html.bsTable = TRUE)
labs %>%
  select(Faculty, Lab, "Recruiting Fall 2021") %>%
  kbl() %>%
  kable_material(c("striped","hover"))
```



